Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-02-21 awipev-CO2.Rmd
added AT analysis since new instrument installed, Nov 2018

#################### Regression function
# function regression plot with model II equation (MA) in title
## Dans labs ajout de la variable title pour mettre title avant chaque graphe
ggreg2 <- function (fit, x, y, point.size=5) { # x and y are the names of the variables
  fit_data <- data.frame(fit$x, fit$y)
  colnames(fit_data) = c(x, y)
reg <- fit$regression.results[2,] #one selects MA only
intercept <- reg$Intercept
slope <- reg$Slope
  ggplot(data = fit_data, aes_string(x = x, y = y)) + 
  geom_point(size = point.size, col = "blue") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3))) +
    theme(plot.title = element_text(size=7))
}

@@

#remove outliers and remove period without TA measurements 
calib_ta_second <- d_all%>%
  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
  dplyr::filter(TA_period == "TA2" & !is.na(at))

@@

#### **Final TA re-calculated data (Salinity relationship)**
```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2450)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

# Property plots : x= at (discretes data), y = at_contros/at_contros_rep/at_calibrated/at_calibrated_rep
```

>>>>

#################### Regression function
# function regression plot with model II equation (MA) in title
## Dans labs ajout de la variable TITRE pour mettre titre avant chaque graphe
ggreg2 <- function (fit, xdata, ydata) { # x and y are the names of the variables
  fit_data <- data.frame(fit$x, fit$y)
  colnames(fit_data) = c(xdata, ydata)
reg <- fit$regression.results[2,] #one selects MA only
intercept <- reg$Intercept
slope <- reg$Slope
  ggplot(data = fit_data, aes_string(x = xdata, y = ydata)) + 
  geom_point(size = 3, col = "blue") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
              colour = "blue")  + 
  labs(title = paste(titre,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3)))
}

mytheme <- theme_bw() +
  theme(axis.text.x=element_text(size=16, color="black"),
        axis.title.x=element_text(face="bold", size=16),
        axis.text.y=element_text(size=16, color="black"),
        axis.title.y=element_text(face="bold", size=16),
        plot.title = element_text(face="bold", size=14)
)

@@

#remove outliers and remove period without TA measurements 
calib_ta_second <- d_all%>%
  dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
  dplyr::filter(TA_period == "TA2" & !is.na(at))

@@

#### **Final TA re-calculated data (Salinity relationship)**
```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2450)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```

There are a lot of outliers in the 4th period (since the new analyzer was set up in Nov. 2018). We use the desplike function to remove them.

#### **TA since November 2018 (final installation)**
```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
# select subset of data and remove obvious outliers
at_nov_2018 <- 
  dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
  filter(datetime > "2018-11-01", AT_filtered > 2250)
#despike
at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
#plot
at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
  geom_point(aes(y=AT_filtered, colour = "before")) +
  geom_point(aes(y=AT_filtered_despike, colour = "after")) +
  labs(x = "Time", y = "Total alkalinity", color = "despike") 
print(at_datetime)

at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
titre <- "Contros AT vs Calculated AT"
fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
```
